### 2012-12-20 inst/examples/myers-exploration.Rmd
30 replicates with full graphs

```{r }
yields <- 
  lapply(1:3, function(j){

@@

## @knitr sim-fish
fish_plot <- ggplot(dt) + 
  geom_line(aes(time, fishstock, group=interaction(reps,method), color=method), alpha=.1) +
  scale_colour_manual(values=cbPalette, guide = guide_legend(override.aes = list(alpha = 1)))
print(fish_plot)

## @knitr sim-harvest
harvest_plot <- ggplot(dt) +
  geom_line(aes(time, harvest, group=interaction(reps,method), color=method), alpha=.1) +
  scale_colour_manual(values=cbPalette, guide = guide_legend(override.aes = list(alpha = 1)))
print(harvest_plot)

>>>>

```{r parallel}
require(snowfall)
sfInit(cpu=2)
sfExportAll()
sfLibrary(pdgControl)
sfLibrary(nonparametricbayes)
sfLibrary(reshape2)
sfLibrary(ggplot2)
sfLibrary(data.table)
sfLibrary(tgp)
sfLibrary(kernlab)
sfLibrary(MCMCpack)
sfLibrary(plyr)
```

```{r }
yields <- 
  sfLapply(1:20, function(j){

@@

## @knitr sim-fish
fish_plot <- ggplot(dt) + 
  geom_line(aes(time, fishstock, group=interaction(reps,method), color=method), alpha=.1) +
  scale_colour_manual(values=cbPalette, guide = guide_legend(override.aes = list(alpha = 1)))+
  ggtitle(paste("rep", j, "seed", seed))
print(fish_plot)

## @knitr sim-harvest
harvest_plot <- ggplot(dt) +
  geom_line(aes(time, harvest, group=interaction(reps,method), color=method), alpha=.1) +
  scale_colour_manual(values=cbPalette, guide = guide_legend(override.aes = list(alpha = 1))) +
  ggtitle(paste("rep", j, "seed", seed))
print(harvest_plot)
